The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-02-10 repeater-vladata.tex
two panel obs figure. using 68% ci for energy distribution

\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline}
\caption{Summary of late-2016 observing coverage and detections of \frb\ during the multi-telescope observing campaign. Symbols show days with observations and circles highlight observations that detected bursts from \frb. Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper). The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes. The solid black line shows the simultaneous burst detection at VLA and Arecibo.
\label{fig:multi}}
\end{center}
\end{figure*}

@@

Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution and best-fit model. We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\propto E^{\alpha}$. Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.4}_{-0.6}$, which is equivalent to a $dN/dE$\ powerlaw index of --1.6. This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit. This is consistent with the high and uniform data quality and the false positive rate in this observing campaign.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{energy_disn}
\caption{Dots and solid line show the  \frb\ burst energy cumulative distribution. The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$. The 95\% bounds on the best-fit powerlaw index is $\alpha=-0.6^{+0.4}_{-0.6}$. \label{fig:ed}}
\end{center}
\end{figure}

>>>>

\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline0}

\includegraphics[width=2\columnwidth]{timeline}
\caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns. Symbols show days with observations and circles highlight observations that detected bursts from \frb. Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper). The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes. The solid black line shows the simultaneous burst detection at VLA and Arecibo.
\label{fig:multi}}
\end{center}
\end{figure*}

@@

Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution and best-fit model. We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\propto E^{\alpha}$. Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.2}_{-0.4}$ (68\% confidence interval), which is equivalent to a $dN/dE$\ powerlaw index of --1.6. This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit. This is consistent with the high and uniform data quality and the false positive rate in this observing campaign.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{energy_disn}
\caption{Dots and solid line show the  \frb\ burst energy cumulative distribution. The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$. The 95\% bounds on the best-fit powerlaw index is $\alpha=-0.6^{+0.2}_{-0.4}$. \label{fig:ed}}
\end{center}
\end{figure}
